\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeSkillsSubheading}[4]{
  \vspace{4pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-17pt}
}


\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{2pt}
}

\newcommand{\resumeExperienceSubheading}[4]{
  \vspace{9pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textbf{#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{2pt}
}


\newcommand{\resumeSubSubheading}[1]{
    \vspace{-15pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} \\
    \end{tabular*}\vspace{2pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Desmond Porth} \\ 
    \small Available in EST, MST, PST, CT timezones \\ \vspace{4pt}
    \small 208-721-7067 $|$ \href{mailto:x@x.com}{\underline{desaporth@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/dporth}{\underline{linkedin.com/in/dporth}} $|$
    \href{https://github.com/dporth}{\underline{github.com/dporth}}
\end{center}

%-----------SKILLS SUMMARY-----------
\section{Skills Summary}
    \begin{minipage}[t]{0.25\textwidth}
        \textbf{Languages} \\
        \textbf{Data Stores} \\
        \textbf{Frameworks \& Tools} \\
        \\
        \\
        \textbf{Methodologies} \\
        \\
        \textbf{Cloud} 
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.74\textwidth}
        Python, SQL, Typescript, Java, PowerShell, Bash, Dart, HTML/CSS \\
        Postgres, SQL Server, Delta Lake \\
        Git, Docker, Spark, PySpark, Databricks, Angular, Kubernetes, JAMS, Flask, Django, Flutter, Jenkins, Octopus, Ansible, DataDog, Grafana, Tableau, Linux  \\
        \\
        Agile, RESTful APIs, Big Data, ETL, CI/CD, Object Oriented Programming, OOP Design Patterns \\
        Azure Databases, APIM, App Service, Blob Storage -- AWS EC2, RDS, S3, OpenSearch -- GCP AutoML Tables, Cloud Functions
    \end{minipage}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeExperienceSubheading
      {Senior Software Engineer}{February 2023 -- Present}
      {Federal Reserve Bank of KC (Remote)}{}
    \resumeSubSubheading
        {Python, SQL, PowerShell, Git, PySpark, Django, Docker, Databricks, Jenkins, OOP, AWS, ETL, REST APIs}{}
      \resumeItemListStart
        \resumeItem{Maintained, enhanced, and optimized the backend of \href{https://www.usaspending.gov/} {\underline{usaspending.gov}} using the tech stack listed above.}
        \resumeItem{Facilitated backend production deployments for usaspending.gov.}
        \resumeItem{Migrated PSQL to Spark SQL and Databricks (on AWS) to decrease the runtime of our nightly ETL pipeline by 7 hours.}
        \resumeItem{Created ETL to load data from Postgres into Elasticsearch to increase the scalability of our API and to ensure fast API response times.}
        \resumeItem{Mentored an intern on the team who ultimately was hired on full time.}
        \resumeItem{Updated ETL pipelines and created new RESTful endpoints to automate generation of unlinked federal award reports so Salesforce could integrate them into our agency resources site.}
      \resumeItemListEnd
      


    \resumeExperienceSubheading
          {Senior Data Engineer}{May 2021 -- February 2023}
          {R1 RCM (Remote)}{}
      \resumeSubSubheading
        {Python, SQL, PowerShell, Git, PySpark, Databricks, Octopus, OOP, JAMS, Docker, ETL, REST APIs}{}
      \resumeItemListStart
        \resumeItem{On a team of 12 Data Engineers, I mentored and led the team to maintain, enhance, and optimize object oriented, batch ETL pipelines in PySpark using Databricks (on Azure).}
        \resumeItem{Refactored our Spark UDFs to Spark function which reduced the runtime of our PySpark DataFrame transformation Microservice by 72\%.}
        \resumeItem{Enabled the re-usability of the company's many Databricks helper notebooks by migrating them to Python libraries with Wheel distributions.}
        \resumeItem{Improved the modularity, scalability, and test-ability of our object oriented inbound pipeline by implementing well known design patterns (Factory, Builder, and Strategy) and best practices/principles (DRY, ETC).}
        \resumeItem{Implemented PySpark queries to support a feature that enabled our inbound object oriented ETL pipeline to ingest keyless visit transactions from hospital systems.}
        \resumeItem{Architect and lead developer of an external facing ETL pipeline, on Databricks, that sped up client implementations and improved data quality of our inbound pipeline.}
        \newline
        \newline
        \newline
    \resumeItemListEnd

   
    \resumeExperienceSubheading
          {Data Engineer}{Feburary 2019 -- May 2021}
          {Micron}{}
      \resumeSubSubheading
        {Python, SQL, Angular, HTML, CSS, PowerShell, Git, Flask, Docker, Jenkins, Kubernetes, ETL, REST APIs}{}
      \resumeItemListStart
        \resumeItem{Developed and maintained a RESTful API using Python, Flask, and SQL Server to enable finance data integration in Salesforce.}
        \resumeItem{Used Docker to containerize Python, Nginx, Angular, R packages, and other data science solutions.}
        \resumeItem{Designed, developed, and maintained end to end solutions including ETL pipelines to ingest data from SAP Hana and Oracle to SQL Server using SSIS, stored procedures, and interactive Tableau dashboards.}
        \resumeItem{Architect and developer of DevOps processes using Jenkins, Groovy, Docker, and OpenShift Kubernetes. My processes served and deployed machine learning models, APIs, and other data science applications.}
        \resumeItem{Created machine learning models using the AutoML Tables API in GCP and integrated the models into data pipelines.}
        \resumeItem{Developed and delivered end to end solutions in the Procurement space like Price Arbitrage, Price Trend, Supplier X-Ray.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Johns Hopkins University}{Online}
      {Master’s in Computer Science}{August 2023 -- Present}
    \resumeSubheading
      {Boise State University}{Graduated Magna Cum Laude (GPA 3.9)}
      {Bachelor of Science in Computer Science, Minor Applied Mathematics}{Earned May 2020}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
